Spending too much time at the Galactic bar: chaotic fanning of the Ophiuchus stream

### 2016-04-15 ms.tex
whitespace and new line in section 3

The orbits sampled from the orbit-fit posteriors in the barred potentials are all strongly chaotic. We have tried computing the frequency diffusion rate for these orbits as an independent check of their chaotic timescale but have found that, over consecutive integration windows, the frequency recovery fails or is unreliable because the frequency spectrum changes dramatically over timescales of $\approx$10--20 orbital periods.

>>>>

The orbits sampled from the orbit-fit posteriors in the barred potentials are all strongly chaotic. We have tried computing the frequency diffusion rate for these orbits as an independent check of their chaotic timescale but have found that, over consecutive integration windows, the frequency recovery fails or is unreliable because the frequency spectrum changes dramatically over timescales of $\approx$10--20 orbital periods. \changes{To understand whether time-dependence or the triaxiality of the bar is the dominant cause of chaos, we have also performed the orbit-fit and Lyapunov time experiments in a potential with a fixed bar ($\Omega_p = 0$) at the same bar angles explored above. We find that the Lyapunov times for orbits fit to the stream in these potentials are consistent with being regular. Computing the frequency diffusion rate instead shows that these orbits are likely weakly chaotic: the frequency diffusion times \citep{apw15-chaos} are $\approx$$10^4~{\rm Gyr}$. We therefore conclude that the time-dependence of the bar is the primary source of chaos in the inner Galaxy.}
